Deconstructing Simple and Choice Decision and Movement Time Across the Spectrum of Schizophrenia Genetic Risk

### 2022-12-20 analysis/paper/elsevier/paper-elsevier.qmd
added arxiv and elsevier quarto extensions again to work better

---
title: "Deconstructing Simple and Choice Decision and Movement Time Across the Spectrum of Schizophrenia Genetic Risk"
author:
  - Joey Trampush:
      correspondence: "yes"
      email: joey.trampush@med.usc.edu
      orcid: 0000-0003-0830-508X
      institute:
        - usc
        - nimh
  - Samantha Fleck:
      institute: usc
      orcid: 0000-0000-0000-0000
  - Dwight Dickinson:
      institute: nimh
      orcid: 0000-0003-1689-0559
  - Juan Pérez:
      orcid: 0000-0003-1689-0551
      institute:
        - name: Acme Corporation
  - Max Mustermann:
      orcid: 0000-0003-1689-0552
institute:
  - ksom:
      name: Keck School of Medicine of USC
      address: 23 Science Street, Eureka, Mississippi, USA
  - nimh: National Institute of Mental Health
title-block-published: "Last updated"  
date: now
date-format: long

format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
  pdf:
    cite-method: biblatex
  arxiv-pdf:
    keep-tex: true  
    linenumbers: false
    doublespacing: false
    runninghead: "Schizophrenia Reaction Time"
    cite-method: biblatex
  arxiv-html: default

execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  schizophrenia; reaction time; keyword 3
highlights: |
  These are the highlights. 
---

>>>>

---
title: "Deconstructing Simple and Choice Decision and Movement Time Across the Spectrum of Schizophrenia Genetic Risk"
author:
  - Joey Trampush:
      correspondence: "yes"
      email: joey.trampush@med.usc.edu
      orcid: 0000-0003-0830-508X
      institute:
        - usc
        - nimh
  - Samantha Fleck:
      institute: usc
      orcid: 0000-0000-0000-0000
  - Dwight Dickinson:
      institute: nimh
      orcid: 0000-0003-1689-0559
  - Juan Pérez:
      orcid: 0000-0003-1689-0551
      institute:
        - name: usc
  - Max Mustermann:
      orcid: 0000-0003-1689-0552
institute:
  - usc:
      name: Keck School of Medicine of USC
      address: 23 Science Street, Eureka, Mississippi, USA
  - nimh: National Institute of Mental Health
title-block-published: "Last updated"  
date: now
date-format: long

format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
  pdf:
    cite-method: biblatex
  arxiv-pdf:
    keep-tex: true  
    linenumbers: false
    doublespacing: false
    runninghead: "Schizophrenia Reaction Time"
    cite-method: biblatex
  arxiv-html: default
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Biological Psychiatry
      formatting: preprint
      model: 3p
      layout: onecolumn
      cite-style: number
      graphical-abstract: "![](abstract.png)"
      highlights:
        - Highlight 1
        - Highlight 2 
        - Highlight 3
    include-in-header: 
      text: |
        \newpageafter{author}

execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  schizophrenia; reaction time; keyword 3
highlights: |
  These are the highlights. 
pdf-engine: pdflatex
pdf-engine-opt: -outdir=elsevier
# order: [abstract, keywords, highlights, title, author, title-block-published, text, colophon, references]
---

### 2022-12-20 analysis/paper/paper-arxiv.qmd
added arxiv and elsevier quarto extensions again to work better

format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
  pdf:
    cite-method: biblatex
  arxiv-pdf:
    keep-tex: true  
    linenumbers: false
    doublespacing: false
    runninghead: "Schizophrenia Reaction Time"
    cite-method: biblatex
  arxiv-html: default
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Biological Psychiatry
      formatting: preprint
      model: 3p
      layout: onecolumn
      cite-style: number
      graphical-abstract: "![](abstract.png)"
      highlights:
        - Highlight 1
        - Highlight 2 
        - Highlight 3
    include-in-header: 
      text: |
        \newpageafter{author}

execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  schizophrenia; reaction time; keyword 3
highlights: |
  These are the highlights. 
pdf-engine: pdflatex
pdf-engine-opt: -outdir=elsevier
# order: [abstract, keywords, highlights, title, author, title-block-published, text, colophon, references]
---

>>>>

format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
  pdf:
    cite-method: biblatex
  arxiv-pdf:
    keep-tex: true  
    linenumbers: false
    doublespacing: false
    runninghead: "Schizophrenia Reaction Time"
    cite-method: biblatex
  arxiv-html: default
  elsevier-pdf:
    keep-tex: true

execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  schizophrenia; reaction time; keyword 3
highlights: |
  These are the highlights. 
---
